Random Forests", OAs

### 2025-02-04 src/oa_RF_corrected.Rmd
oa

# For growth:
df <- df %>% group_by(oa11cd) %>% 
  mutate(#n.lag = dplyr::lag(n),
         growth = log(n/n.lag),
                    abs.growth = n - n.lag) %>% 
  relocate(n.lag, .after = n)

@@

start.time <- Sys.time()
model.all <- train(n ~ #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                     n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                     #London.v + city.v + retail.v + n.l.slag + year,
                   data = df, 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.283708  0.3202280  1.034153
#   2     extratrees  3.516978  0.2323646  1.087689
#   5     variance    3.240309  0.3354508  1.019184
#   5     extratrees  3.443571  0.2565672  1.107110
#   8     variance    3.278693  0.3251487  1.017672
#   8     extratrees  3.449965  0.2562403  1.124713
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance and min.node.size = 5.

@@

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

>>>>

# For growth:
df <- df %>% group_by(oa11cd) %>% 
  mutate(#n.lag = dplyr::lag(n),
         growth = log(n/n.lag),
                    abs.growth = n - n.lag) %>% 
  relocate(n.lag, .after = n) %>% 
  ungroup()

@@

start.time <- Sys.time()
model.all <- train(n ~ #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                     n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                     #London.v + city.v + retail.v + n.l.slag + year,
                   data = df, 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.235219  0.3131576  1.211443
#   2     extratrees  3.452069  0.2176445  1.182582
#   5     variance    3.217974  0.3337214  1.233777
#   5     extratrees  3.386142  0.2500448  1.251388
#   8     variance    3.294155  0.3208588  1.240884
#   8     extratrees  3.418390  0.2496608  1.281916
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule
#  = variance and min.node.size = 5.

@@

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",,
                   num.threads = 15)

### 2025-02-04 src/oa_RF_corrected_10.Rmd
oa

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df, 
                                spacevar = "oa11cd",
                                timevar = "year", 
                                k = 10)

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    22.46734  0.4784290  5.681843
#   2     extratrees  24.69943  0.3875775  6.049473
#   5     variance    22.50225  0.4803563  5.664478
#   5     extratrees  23.95316  0.4143508  6.102471
#   8     variance    23.14682  0.4644807  5.678126
#   8     extratrees  24.14426  0.4095256  6.213216
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD!=i), 
                                spacevar = "oa11cd",
                                timevar = "year", 
                                k = k)

@@

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

>>>>

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df, 
                                spacevar = "RGN11CD",
                                timevar = "year", 
                                k = 10)

#length is = (n_repeats*nresampling)+1
seeds <- vector(mode = "list", length = 8)

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    21.61442  0.4482161  6.736518
#   2     extratrees  23.82034  0.3557068  6.584642
#   5     variance    21.58205  0.4549608  6.845549
#   5     extratrees  23.00958  0.3848122  6.884375
#   8     variance    22.07397  0.4426922  6.949996
#   8     extratrees  23.17989  0.3796106  7.060913
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule
#  = variance and min.node.size = 5.

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD!=i), 
                                spacevar = "RGN11CD",
                                timevar = "year", 
                                k = k)

@@

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)
